---
title: "eds212_day5_comp1"
format: 
  html: 
    code-fold: true # puts code into a dropdown
    code-summary: "show me the code"
editor: visual
execute: 
  echo: true # whether code shows up or not
  warning: false # whether messages like running tidyverse shows up
---

```{r}
library(tidyverse)
```

Explore starwars dataset- first 6 lines, dimensions, histogram of heights, scatterplot of height vs. weight

```{r}
head(starwars)

dim(starwars)

names(starwars)
```

```{r}
ggplot(data = starwars, 
       aes(x = height)) +
  geom_histogram(color = "purple", fill = "orange") +
  theme_dark()
```

```{r}
ggplot(data = starwars,
       aes(x = height,
           y = mass)) +
  geom_point(color = "orange") +
  theme_dark() + # theme
  labs(x = "height in cm",
      y = "mass in kg",
      title = "height vs mass of starwars characters") # labels
```

```{r}
starwars$height # pull out the vector of all the values for height

class(starwars$height) # check the class for the values in height
```

calculate summary statistics

use mean() to find means and sd() to find standard deviations

```{r}
# na.rm removes NA values
mean_height <- mean(starwars$height, na.rm = TRUE)
```

find and store sd

```{r}
sd_height <- sd(starwars$height, na.rm = TRUE)
```

## In-line reporting using code outputs

-   good for reproducibility

the mean height of star wars character is `r mean_height` cm with a standard deviation of `r sd_height` cm
